Glasshouse experiment

### 2018-07-11 Rmd/ms_draft.Rmd
changes

**Paragraph 1**

A common trend in natural ecosystems is pollinator sharing (REF). Therefore, pollen from different species can arrive to the stigmas of other species. The real impact of pollen in a natural ecosystem is still unknown. Nonetheless, some advances has been done with recent works where heterospecific pollen effect has been evaluated (REFS).

**Paragraph 2**

@@

The study was conducted in a glasshouse at University of New England (Armidale, Australia). Rooms were temperature controlled depending on the requirements of the species. The species selected belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae. The criteria of species selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), easy species to grow, low structural flower complexity. For the purpose of the experiment all the species where consider as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

@@

Check fertiliser type: Hortico (all purpose soluble fertiliser) NPK 23: 3.95: 14

Table of species:

@@

```{r, echo=FALSE}

#OVYLE NUMBER OF THE DIFFERENT SPECIES N=15

library(reshape2)

# Consider NA's as 0, I have to double check this

ovules <- read.csv("Ovules.csv", sep=";")

#plot(ovules)

mean_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = mean, data = ovules, na.rm= TRUE)

colnames(mean_ovule)[2] <- "avg"

sd_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = sd, data = ovules, na.rm= TRUE)

colnames(sd_ovule)[2] <- "sdev"

x <- 1:8

plot(x, mean_ovule$avg,
     ylim=range(c(mean_ovule$avg-sd_ovule$sdev, mean_ovule$avg+sd_ovule$sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="N of Ovules")
# hack: we draw arrows but with very special "arrowheads"
arrows(x, mean_ovule$avg-sd_ovule$sdev, x, mean_ovule$avg+sd_ovule$sdev, length=0.05, angle=90, code=3)

axis(x, at=1:8, labels = mean_ovule$Species,cex=0.2, tick = FALSE, padj= -0.5, side = 1)

**Seed set Petunia**

```{r, echo=FALSE}
library(reshape2)

# Consider NA's as 0, I have to double check this

seed_set <- read.csv("PEIN_seed_set.csv", sep=";")

#Delete Cross with lost seeds
seed_set[c(12,17,19),4] <- NA
#Deleted

mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = seed_set, na.rm= TRUE)

mean_seed_seet$.-> avg

sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = seed_set, na.rm= TRUE)

sd_seed_seet$. -> sdev

sdev[4] <- 0

#plot(seed_set, cex.axis=0.5)

x <- 1:7

plot(x, avg,
     ylim=range(c(avg-sdev, avg+sdev)),
     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
     main="PEIN seed set"
)
# hack: we draw arrows but with very special "arrowheads"
arrows(x, avg-sdev, x, avg+sdev, length=0.05, angle=90, code=3)

axis(x, at=1:7, labels = mean_seed_seet$Treatment,cex.axis=0.8, tick = FALSE, padj= -0.5, side = 1)

>>>>

**Paragraph 1** Introduction to the topic

Flowerings plants depend highly on animal vectors to be pollinated (Ollerton et al, 2011) and their coevolutive history has lead to a great diversity of floral structures (Refs). Generally these different plant species coexist together in natural ecosystems where they compete for pollinators (Refs) or facilitate pollinator's visitation. In addition, pollinator sharing is a common feature in natural ecosystems (Ref) and therefore plant species will recieve conspecific pollen but also heterospecific pollen or interspecific pollen (HP or IP).

Vamosi species limited by pollen

**Paragraph 2** Research on the topic so far

@@

The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018. Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences. The species selected (Table 1) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae. The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), low structural flower complexity and fast life cycle. For the purpose of the experiment all the species where consider as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

**Table 1**
```{r}

**Hand-pollination**

Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Had-pollination was realized with 3-4 gentle touches on the surface of the stigma. The mixes of pollen were performed based on the pollen counts on an eppendorf. Pollen on anthers was counted through Neubaeur chamber.

@@

@@
